---
title: "Airbnb LA data"
author: "Ryan Mezera"
date: "April 24, 2019"
output: html_document
---
# Airbnb LA Data Analysis

Here we will do some data analysis for the Airbnb LA data.  The primary goal will be to make some graphics to be used in a presentation.


```{r setup}
df = read.csv('df_final.csv')

df_stats = read.csv('daily_stats.csv')
```

```{r packages}
library(GGally)
library(ggplot2)
library(gridExtra)
```

## Price

Here we will make a number of visualizations related to price

```{r}

ggplot(data = df,
       aes(x = price))+
  geom_histogram(bins = 30)+
  labs(title='Price Distribution')

```

```{r}
  #Boxplot
ggplot(data = df,
       aes( x = 1, y = price) ) + 
  geom_jitter(alpha = 0.3 ) +
  geom_boxplot(alpha = 0.2, color = 'red' )
```

#### Here we will compare price statistics from different cities

```{r}
cities_high = c('Malibu', 'Hawthorne', 'Santa Monica', 'Manhattan Beach', 'Torrance', 'Culver City', 'Venice', 'Alhambra')
cities_low = c('Redondo Beach', 'Altadena', 'Burbank', 'Topanga', 'San Gabriel','Monterey Park', 'Glandale', 'Temple City', 'Inglewood')

```

```{r}
  #Bivariate boxplot with quality as factor
ggplot(aes(city, 
           price), 
       data = df[df$city==cities_low,]) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)+
  ylim(0,1000)+
  xlab('City')+
  ylab('Price')+
  labs(title='Low Price Cities')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



```{r}
  #Bivariate boxplot with quality as factor
ggplot(aes(city,price), 
       data = df[df$city==cities_high,]) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)+
  ylim(0,1000)+
  xlab('City')+
  ylab('Price')+
  labs(title='High Price Cities')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```





# Occupancy ratio

Here we will make a number of vizualizations that relate to occupancy ratio

```{r}
ggplot(data = df,
       aes(x = occupancy_ratio))+
  geom_histogram(bins = 30)+
  labs(title='Occupancy Ratio Distribution')
```


```{r}
ggplot(data = df,
       aes(y=occupancy_ratio,x=host_listings_count))+
  geom_point(alpha = 0.1)+ 
    ggtitle('Occupancy Ratio vs Host Listings Counts')+
    xlab('Host Listings Counts')+
    ylab('Occupancy Ratio')
```

# Review scores

Here we will make a number of vizualizations that relate to review scores rating


```{r}
ggplot(data = df,
       aes(x = review_scores_rating))+
  geom_histogram(bins = 30)+
  labs(title='Review Score Rating Distribution')
```


```{r}
ggplot(data = df,
       aes(y=review_scores_rating,x=host_listings_count))+
  geom_point(alpha = 0.1)+ 
    ggtitle("Review Scores Rating vs Host Listings Count")+
    xlab('Host Listings Count')+
    ylab('Review Scores Ratings')
```











